Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-12-05 pkg/circtree/inst/wind_paper/draft/draft.Rnw
minor corrections
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2917 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3c87c57b37758f4a74fded0955ca83045888ca7a

\begin{appendix}

\section{Tree algorithm}
\label{app:algorithm}
This section provides a more detailed overview on the permutation-test-based CTree algorithm 
\citep{Hothorn+Hornik+Zeileis:2006}, 
specifically for circular data as applied for building circular regression trees and forests 
as presented in this case study. 
An alternative tree-building framework is provided by the MOB algorithm, which is based on 
M-fluctuation tests \citep[see][for more details]{Zeileis+Hothorn+Hornik:2008}.

>>>>

\newpage
\begin{appendix}

\section{Tree algorithm}
\label{app:algorithm}
This section provides a more detailed overview on the permutation-test-based CTree algorithm 
\citep{Hothorn+Hornik+Zeileis:2006}, 
specifically for circular data as applied for building circular regression trees and forests 
presented in this case study. 
An alternative tree-building framework is provided by the MOB algorithm, which is based on 
M-fluctuation tests \citep[see][for more details]{Zeileis+Hothorn+Hornik:2008}.
